### 2013-11-25 PositionPaper/relwork.tex

The advent of cloud computing imposed a new model for resource managing.
The new model is not concerned with the \textit{limits} of resource availability but with the \textit{technical and economic} conditions to be fulfilled in order to access a potentially infinite set of resources. 
Service Level Agreements (SLA)~\cite{SLA} can be used in thee context of cloud computing in order to establish those conditions.
SLAs are bounding contracts between each service provider and their clients.
The deployment of SLAs lies on two features: (i) the negotiation of conditions, agreed by both parts and (ii) the monitoring of these conditions during the use of each service.

=====================
Recent research works on SLA are devoted to the SLA extension to security concerns. Hale
and al. in \cite{6274042} propose an extension of the WSAgreement initially developed by the GRAAP
working group. The extension allows security constraints to be expressed over the service description
terms (SDTs) and the service level objectives (SLOs) of the SLA. Consequently, this leads to a certain kind of security expression interoperability and lets the client to be able to compare security level of different CSP. Luna and al
work \cite{LunaGarcia:2012:BCS:2381913.2381932} focuses on how to build a SEcSLA Template starting from gathering then categorizing a set of security statements using a semantic tool. The designed template is then used both to express user security requirements and CSP security provisions.

>>>>

The advent of cloud computing imposed a new model for resource managing.
The new model is not concerned with the \textit{limits} of resource availability but with the \textit{technical and economic} conditions to be fulfilled in order to access a potentially infinite set of resources. 
Service Level Agreements (SLA)~\cite{SLA} can be used in thee context of cloud computing in order to establish those conditions.
SLAs are bounding contracts between each service provider and their clients.
The deployment of SLAs relies on two principles: (i) The negotiation of conditions, which are statically agreed between the parts and (ii) The monitoring of these conditions during the use of each service.

The agreed conditions should be explicit and quantifiable.
They should be part of the contract between the client and the service provider.
Their quantifiable nature makes it possible for the conditions to appear as non-functional requirement to be imposed to each individual service.

Monitoring SLAs is normally part of the infrastructure provided by the cloud.
The user may verify that the service complies with the agreed SLA.

=====================

Recent research works on SLA are devoted to the SLA extension to security concerns. Hale
and al. in \cite{6274042} propose an extension of the WSAgreement initially developed by the GRAAP
working group. The extension allows security constraints to be expressed over the service description
terms (SDTs) and the service level objectives (SLOs) of the SLA. Consequently, this leads to a certain kind of security expression interoperability and lets the client to be able to compare security level of different CSP. Luna and al
work \cite{LunaGarcia:2012:BCS:2381913.2381932} focuses on how to build a SEcSLA Template starting from gathering then categorizing a set of security statements using a semantic tool. The designed template is then used both to express user security requirements and CSP security provisions.
